Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-09-21 manuscript/manuscript.tex
Edited grid table and its description

\begin{table}
\caption{
    Description of the tesseroid models of a spherical shell and computation grids
    used to characterize the accuracy of the numerical integration.
    Every grids consist of a set of $10 \times 10$ points.
}
\label{tab:grids}
\begin{tabular}{lccc}
    Name & Tesseroid size & Grid region (degrees) & Grid height (km)
    \\ \hline
    Pole & $1^\circ \times 1^\circ$ & $0\text{E}/1\text{E}/89\text{N}/90\text{N}$ & 2 \\
    Equator & $1^\circ \times 1^\circ$ & $0\text{E}/1\text{E}/0\text{N}/1\text{N}$ & 2 \\
    Satellite & $1^\circ \times 1^\circ$ & $0\text{E}/1\text{E}/89\text{N}/90\text{N}$ & 260 \\
    Big Grid & $30^\circ \times 30^\circ$ & $0\text{E}/30\text{E}/60\text{N}/90\text{N}$ & 2 \\
\end{tabular}
\end{table}

>>>>

\begin{table}
\caption{
    Description of computation grids used to characterize the accuracy of
    the numerical integration.
    Every grid consist of a set of $10 \times 10$ points.
}
\label{tab:grids}
\begin{tabular}{lccc}
    Name & Grid region (degrees) & Grid height (km)
    \\ \hline
    Pole & $0\text{E}/1\text{E}/89\text{N}/90\text{N}$ & 2 \\
    Equator & $0\text{E}/1\text{E}/0\text{N}/1\text{N}$ & 2 \\
    Satellite & $0\text{E}/1\text{E}/89\text{N}/90\text{N}$ & 260 \\
    Big Grid & $0\text{E}/30\text{E}/60\text{N}/90\text{N}$ & 2 \\
\end{tabular}
\end{table}
